A Decision Procedure for (Co)datatypes in SMT Solvers

### 2016-02-24 jour/jour.tex
Finish examples to supplment solution soundness.

\begin{examplex}
\label{ex:assign-complete}
Continuing with Example~\ref{ex:assign}, while extending $\Val$ to its corresponding completion $\ValC$,
we may, for instance, assign $\MU {\Varec{z}}.\; \const{E}( {\Varec{z}} )$ to $\Varec{z}$,
and subsequently assign $\MU {\Varec{y}}.\; \const{D}( {\Varec{y}} )$ to $\Varec{y}$.
We obtain the following mapping $\ValC$ from equivalence classes to $\MU$-terms:
\[\begin{array}{r@{}c@{}r@{}l@{\qquad}r@{}c@{}r@{}l@{\qquad}r@{}c@{}l}
\ValC \ec{u} & {}\,=\,{} & \MU {\Varec{u}}.\; & \const{C}( \MU {\Varec{z}}.\; \const{E}( {\Varec{z}} ) ) &
\ValC \ec{w} & = & \MU {\Varec{w}}.\; & \const{E}( \MU {\Varec{y}}.\; \const{D}( {\Varec{y}} ) ) &
\ValC \ec{y} & {}\,=\,{} & \MU {\Varec{y}}.\; \const{D}( {\Varec{y}} ) \\
\ValC \ec{v} & = & \MU {\Varec{v}}.\; & \const{D}( \MU {\Varec{z}}.\; \const{E}( {\Varec{z}} ) ) &
\ValC \ec{x} & {}\,=\,{} & \MU {\Varec{x}}.\; & \const{C}( \MU {\Varec{v}}.\; \const{D}( \MU {\Varec{z}}.\; \const{E}( {\Varec{z}} ) ) ) &
\ValC \ec{z} & = & \MU {\Varec{z}}.\; \const{E}( {\Varec{z}} )
\end{array}\]
Notice that $\ValC$ satisfies the properties from Lemma~\ref{lem:interpretation-completion} for a normal interpretation $\J$:
all terms in the range of $\ValC$ are closed and normal, 
$\ValC \ec{s} = \expand{\ValC \ec{y}}{ t }$ for all subterms $t$ where $\muvar(t) = {\Varec{s}}$ for all $s$,
and all terms in the range of $\ValC$ are pairwise alpha-disequivalent.
We may construct an interpretation $\J$ where variables are assigned the value
that is alpha-equivalent to one from $\interp{\J}{\delta}$, and is uniquely associated to its equivalence class by $\ValC$.
For instance, up to renaming,
$\interp{\J}{u}$ is $\const{C}( \MU {\Varec{z}}.\; \const{E}( {\Varec{z}} ) )$,
$\interp{\J}{v}$ and $\interp{\J}{s}$ are $\const{D}( \MU {\Varec{z}}.\; \const{E}( {\Varec{z}} ) )$, and so on.
\xend
\end{examplex}

@@

>>>>

\begin{examplex}
\label{ex:assign-complete}
Consider $\Val$ from Example~\ref{ex:assign}.
While extending $\Val$ to its corresponding completion $\ValC$,
we may, for instance, assign $\MU {\Varec{z}}.\; \const{E}( {\Varec{z}} )$ to $\Varec{z}$,
and subsequently assign $\MU {\Varec{y}}.\; \const{D}( {\Varec{y}} )$ to $\Varec{y}$.
We obtain the following mapping $\ValC$ from equivalence classes to $\MU$-terms:
\[\begin{array}{r@{}c@{}r@{}l@{\qquad}r@{}c@{}r@{}l@{\qquad}r@{}c@{}l}
\ValC \ec{u} & {}\,=\,{} & \MU {\Varec{u}}.\; & \const{C}( \MU {\Varec{z}}.\; \const{E}( {\Varec{z}} ) ) &
\ValC \ec{w} & = & \MU {\Varec{w}}.\; & \const{E}( \MU {\Varec{y}}.\; \const{D}( {\Varec{y}} ) ) &
\ValC \ec{y} & {}\,=\,{} & \MU {\Varec{y}}.\; \const{D}( {\Varec{y}} ) \\
\ValC \ec{v} & = & \MU {\Varec{v}}.\; & \const{D}( \MU {\Varec{z}}.\; \const{E}( {\Varec{z}} ) ) &
\ValC \ec{x} & {}\,=\,{} & \MU {\Varec{x}}.\; & \const{C}( \MU {\Varec{v}}.\; \const{D}( \MU {\Varec{z}}.\; \const{E}( {\Varec{z}} ) ) ) &
\ValC \ec{z} & = & \MU {\Varec{z}}.\; \const{E}( {\Varec{z}} )
\end{array}\]
Notice that $\ValC$ satisfies the properties from Lemma~\ref{lem:interpretation-completion} for a normal interpretation $\J$:
all terms in the range of $\ValC$ are closed and normal, 
$\ValC \ec{s} = \expand{\ValC \ec{y}}{ t }$ for all subterms $t$ where $\muvar(t) = {\Varec{s}}$ for all $s$,
and all terms in the range of $\ValC$ are pairwise alpha-disequivalent.
We may construct an interpretation $\J$ where variables are interpreted as the value
that is alpha-equivalent to one from $\interp{\J}{\delta}$, and is uniquely associated to its equivalence class by $\ValC$.
%For instance, up to renaming,
%$\interp{\J}{u}$ is $\const{C}( \MU {\Varec{z}}.\; \const{E}( {\Varec{z}} ) )$,
%$\interp{\J}{v}$ and $\interp{\J}{s}$ are $\const{D}( \MU {\Varec{z}}.\; \const{E}( {\Varec{z}} ) )$, and so on.
\xend
\end{examplex}

@@

\begin{examplex}
\label{ex:model}
Continuing Example~\ref{ex:assign-complete}, let $\J$ be a normal interpretation, where
up to renaming of $\MU$-bound variables, we have:
\[\begin{array}{r@{}c@{}r@{}c@{}l@{\qquad}r@{}c@{}l@{\qquad}r@{}c@{}l}
& &\interp{\J}{u} & {}\,=\,{} &  \const{C}( \MU {\Varec{z}}.\; \const{E}( {\Varec{z}} ) ) &
\interp{\J}{w} & = &  \const{E}( \MU {\Varec{y}}.\; \const{D}( {\Varec{y}} ) ) &
\interp{\J}{y} & {}\,=\,{} & \MU {\Varec{y}}.\; \const{D}( {\Varec{y}} ) \\
\interp{\J}{v} & = & \interp{\J}{s} & = & \const{D}( \MU {\Varec{z}}.\; \const{E}( {\Varec{z}} ) ) &
\interp{\J}{x} & {}\,=\,{} & \const{C}( \const{D}( \MU {\Varec{z}}.\; \const{E}( {\Varec{z}} ) ) ) &
\interp{\J}{z} & = & \MU {\Varec{z}}.\; \const{E}( {\Varec{z}} )
\end{array}\]
It can be shown $\J$ satisfies $\Ec =
\{
u \teq \const{C}( z ),\;
v \teq \const{D}( z ),\;
w \teq \const{E}( y ),\;
x \teq \const{C}( v ),\;
v \teq s,\;
z \not\teq v
\}$.
\xend
\end{examplex}
